\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{mathrsfs,amsmath}
\usepackage{float}
\usepackage{subfig}
\usepackage{graphicx}


% Puts captions of tables on top
\floatstyle{plaintop}
\restylefloat{table}

% Puts captions in bold
\captionsetup{labelfont=bf}

\title{Wavefront Sensing}

\begin{document}
\maketitle

\input{Introduction}
\input{FraunhoferApprox}
\input{DFT}
\input{ImgSys}
\input{Pupil}
\input{Noise}
\input{LensletArray}

\begin{thebibliography}{9}

\bibitem{CFO}
D. Voelz, \textit{Computational Fourier Optics}. SPIE Press, 2011.

\bibitem{NSOWP}
J.D. Schmidt, \textit{Numerical Simulation of Optical Wave Propagation with examples in Matlab (SPIE Press Monograph Vol. PM199)}. SPIE Press, Aug. 2010.

\bibitem{AOLectureNotes}
M. Verhaegen, "Lecture notes on control for High Resolution Imaging," May 2012.

\bibitem{RayleighFigure}
Pinhole Works. (2014, May 12). \textit{Goerge Airy vs. Lord Rayleigh} [Online]. Available: http://pinholeworks.com/wp/goerge-airy-vs-lord-rayleigh/

\bibitem{NumSimCCD2011}
M.V. Konnik and J.S. Welsh, "On numerical simulation of high-speed CCD/CMOS-based wavefront sensors for adaptive optics,"
\textit{Proc. SPIE 8149},
September 2011.

\bibitem{WFCorr2013}
C.S. Smith et al., "Iterative linear focal-plane wavefront correction,"
\textit{J. Opt. Soc. Am. A}, vol. 30, no. 10, pp. 2002-2011, 
October 2013.

\bibitem{SHWFS2006}
L. Gilles and B. Ellerbroek, "Shack-Hartmann wavefront sensing with elongated sodium laser beacons: centroiding versus matched filtering,"
\textit{Applied Optics}, vol. 45, no. 25, pp. 6568-6576, 
September 2006.

\bibitem{AccHS1994}
G. Cao and X. Yu, "Accuracy analysis of a Hartmann-Shack wavefront sensor operated with a faint object," 
\textit{Optical Engineering}, vol. 33(7), pp. 2331-2335, 
July 1994. 



\end{thebibliography}


\end{document}